A Data-Driven Early Warning System for Mining Accident

### 2017-03-20 San Antonio/presentation_materials.Rmd
slides first draft

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

@@

```{r top 10 fatality}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.deaths <- complete.active.quarters %>% filter(active & year >= 2005) %>% arrange(desc(num.death)) %>% select(mine.name, mine_id, year, quarter, num.death)
head(top.deaths, 10)
```
### Top 10 Causes of Death Since 2005
```{r top 10 causes of death}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & cal_yr >= 2005) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)
```

@@

Among the top 10 mine-quarters based on number of days lost,
```{r top 10 days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.days.lost <- complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost)) %>% select(mine.name, year, quarter, num.days.lost)
head(top.days.lost, 10)
```
the "American Coal Company New Era Mine" take 5 spots.
Let's take a look at its second quarter of 2005:
```{r new era}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc
    #ai_occ_desc 
    #ai_narr
    ) 
head(new.era)
```
In particular, the top accident was:
```{r new era accident 1}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr,
    inj_degr_desc
    ) 
print(as.character(new.era.top.accidents$ai_narr[1]))
print(as.character(new.era.top.accidents$inj_degr_desc[1]))
```
and the second to top accident was:
```{r new era, accident 2}
if(!exists("new.era.top.accidents")){
 if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr
    )  
}
print(as.character(new.era.top.accidents$ai_narr[2]))
print(as.character(new.era.top.accidents$inj_degr_desc[2]))
```

## Statistical Models

@@

The following linear model tests a few predictors and their ability to predict number of days lost or restircted:
```{r simple lm of days lost/restricted}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
num.days.lm <- lm(0*num.death+1*num.days.lost+1*num.days.restrict~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active))
summary(num.days.lm)
```
The following linear model tests a few predictors and their ability to predict number of deaths:
```{r simple lm of death}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
num.deaths.lm <- lm(1*num.death+0*num.days.lost+0*num.days.restrict~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active))
summary(num.deaths.lm)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

@@

```{r top 10 fatality}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.deaths <- complete.active.quarters %>% filter(active & year >= 2005) %>% arrange(desc(num.death), mine.name) %>% select(mine.name, mine_id, year, quarter, num.death)
head(top.deaths, 10)
```
### Top 10 Causes of Death Since 2005
```{r top 10 causes of death}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & cal_yr >= 2005) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)
```

@@

Among the top 10 mine-quarters based on number of days lost,
```{r top 10 days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.days.lost <- complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost), mine.name) %>% select(mine.name, mine_id, year, quarter, num.days.lost)
head(top.days.lost, 10)
```
the "American Coal Company New Era Mine" take 5 spots.
Let's take a look at its second quarter of 2005:
```{r new era}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc
    #ai_occ_desc 
    #ai_narr
    ) 
head(new.era)
```
In particular, the top accident was:
```{r new era accident 1}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr,
    inj_degr_desc
    ) 
print(as.character(new.era.top.accidents$ai_narr[1]))
print(as.character(new.era.top.accidents$inj_degr_desc[1]))
```
and the second to top accident was:
```{r new era, accident 2}
if(!exists("new.era.top.accidents")){
 if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr
    )  
}
print(as.character(new.era.top.accidents$ai_narr[2]))
print(as.character(new.era.top.accidents$inj_degr_desc[2]))
```

## Statistical Analyses

### Severe Accidents

```{r severe}
# options(digits = 1)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
severe.summary <- complete.active.quarters %>%
  filter(active) %>%
  mutate(severe = ifelse(
    num.death + num.dis > 0, TRUE, FALSE
  )) %>%
  group_by(severe) %>%
  summarise(n = n()) %>%
  mutate(perc = n / sum(n) * 100)
print(severe.summary)
```

### Fixed Effects Model with Combined Data (training = testing)

```{r fe.cmb}
if (!exists("fe.cmb.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.cmb.result %>% filter(year >= 2005) %>% arrange(desc(num.death), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
head(fe.cmb.result %>% filter(year >= 2005) %>% arrange(desc(prob), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
print(fe.cmb.performance)
```

### Fixed Effects Model with Divided Data (half training, half testing)

```{r fe.div}
if (!exists("fe.div.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.div.result %>% filter(year >= 2005) %>% arrange(desc(num.death), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
head(fe.div.result %>% filter(year >= 2005) %>% arrange(desc(prob), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
print(fe.div.performance)
```

### Logistic Regression Model without Fixed Effects

```{r glm}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(glm.result %>% filter(year >= 2005) %>% arrange(desc(num.death), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
head(glm.result %>% filter(year >= 2005) %>% arrange(desc(prob), mine.name), 20) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
print(glm.performance)
```

@@

The following linear model tests a few predictors and their ability to predict number of days lost or restircted:
```{r simple lm of days lost/restricted}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
num.days.lm <- lm(0*num.death+1*num.days.lost+1*num.days.restrict~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active))
summary(num.days.lm)
```
The following linear model tests a few predictors and their ability to predict number of deaths:
```{r simple lm of death}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
num.deaths.lm <- lm(1*num.death+1*num.dis +0*num.days.lost+0*num.days.restrict~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active))
summary(num.deaths.lm)
```

### 2017-03-20 San Antonio/slides/presentation_slides.Rmd
slides first draft

---
title: "A Data-Driven Early Warning System for Mining Accident"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shiva Rajgopal, Vinay Ramesh,
  | Venkat Venkatasubramanian, Zhizun Zhang, and Catherine Zhao
shortauthor: "Luo et al."
institute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    # incremental: true
    template: rmd_template.tex
    fig_height: 4.75
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

# Introduction: Mine Safety and MSHA Data

@@

## Upper Big Branch Disaster

# Methods: Data and Model Assumptions

@@

- **Mine accidents**: "msha_accident.csv" (681,386 obs., retrieved 1/26/2017, from <https://enforcedata.dol.gov/views/data_summary.php>)
- **MSHA assessed violations**: "AssessedViolations.csv" (2,169,804 obs., retrieved 12/10/2016, from <https://arlweb.msha.gov/OpenGovernmentData/OGIMSHA.asp>)

@@

## Model

@@

## Number of Days Lost since 2000

```{r num.days.lost trend}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.lost <- complete.active.quarters %>% 
  filter(year >= 2000 & active) %>%
  group_by(year) %>%
  summarise(count = sum(num.days.lost),
            avg = mean(num.days.lost))
qplot(x = year, y = count, data = yearly.lost, geom = c("point", "line"),
      main = "Number of Total Days Lost Due to Accidents",
      xlab = "Year", ylab = "Count")
# qplot(x = year, y = avg, data = yearly.lost, geom = c("point", "line"),
#       main = "Number of Average Days Lost Due to Accidents",
#       xlab = "Year", ylab = "Count")
```

## Number of Violations since 2000

```{r viol.quantity trend}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(year >= 2000 & active) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity),
            avg = mean(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Total Violations",
      xlab = "Year", ylab = "Count")
```

@@

>>>>

---
title: "A Data-Driven Early Warning System for Mining Accident"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shiva Rajgopal, Vinay Ramesh,
  | Venkat Venkatasubramanian, Zhizun Zhang, and Catherine Zhao
shortauthor: "Luo et al."
institute: |
  | Chemical Engineering, Computer Science, and Business School
  | Columbia University
shortinstitute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    keep_tex: false
    incremental: false
    template: rmd_template.tex
    fig_height: 4.75
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, fig.align = "center")
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

## Complex, Resilient, Intelligent Systems (CRIS Lab)

![CRIS Lab](CrisResearch720.png)

<!-- https://aiche.confex.com/aiche/s17/webprogram/Paper480429.html -->
# Introduction: A Data Approach to Mine Safety

## Systemic Risk

- Systemic disasters
    - SARS (2003)
    - Northeast Blackout (2003)
    - Subprime Crisis (2008)
    - Deepwater Horizon Oil Spill (2010)
- Emerging systemic risks
    - Climate change
    - Income/wealth inequality
    - Cyber-physical security
    - Technological singularity
- Fast-paced and connected
- Design complex systems
- Analyze systemic risk

<!-- 
https://en.wikipedia.org/wiki/Upper_Big_Branch_Mine_disaster
https://arlweb.msha.gov/MEDIA/PRESS/2011/NR111206.asp 
-->
## Upper Big Branch Mine Disaster (2010)

- April 5, 2010, Raleigh County, West Virginia, owned by Massey Energy
- 29 deaths, the worst mining in the United States since 1970
- MSHA cites corporate culture as root cause of Upper Big Branch Mine disaster

## Sago Mine Disaster (2006)

- January 2, 2006, Sago, West Virginia, owned by Anker West Virginia Mining
- 13 miners were trapped for nearly two days; only one survived
- Fatality number was exceeded by the Upper Big Branch Mine disaster
- MSHA reports prior history of safety violations and fatalities

@@

## Can We Further Improve Mine Safety?

- Process MSHA safety data
- Understand the underlying causal relationships
- Develop early warning systems

# Methods: Data Sources and Model Preliminaries

@@

- Mine accidents table: "msha_accident.csv" 
    - 681,386 rows
    - Retrieved 1/26/2017, from <https://enforcedata.dol.gov/views/data_summary.php>
- MSHA assessed violations table: "AssessedViolations.csv" 
    - 2,169,804 rows
    - Retrieved 12/10/2016, from <https://arlweb.msha.gov/OpenGovernmentData/OGIMSHA.asp>

- 664,128 rows
- 10,377 unique mines
- From 2000 to 2015 in quarters
- Each row represents data for a unique combination of mine, year, and quarter
    - e.g., Upper Big Branch Mine in the second quarter of 2010
- Each row contains both current and past information

@@

## Top 10 Fatal Accidents Since 2005

```{r top 10 fatality}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.deaths <- complete.active.quarters %>% filter(active & year >= 2005) %>% arrange(desc(num.death), mine.name) %>% select(mine.name, mine_id, year, quarter, num.death)
head(top.deaths, 10)
```

## Violation Trend: Upper Big Branch

```{r upper big branch}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608436 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Violation Trend: Sago Mine

```{r sago}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608791 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Violation Trend: Crandall Canyon

```{r crandall}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Violation Trend: Darby Mine No. 1

```{r darby}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1518185 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Violation Trend: Gibson

```{r gibson}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1202215 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Predictive Model

- Rising violation trends before disasters
- A disaster classifier based on historical data?
- Define a **severe** accident as one with death or permenant disability
- Unbalanced data

```{r severe all}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
severe.summary <- complete.active.quarters %>%
  filter() %>%
  mutate(severe = ifelse(
    num.death + num.dis > 0, TRUE, FALSE
  )) %>%
  group_by(severe) %>%
  summarise(n = n()) %>%
  mutate(perc = n / sum(n) * 100)
print(severe.summary)
```

@@

## Processing Data

- Remove **inactive** quarters

```{r severe active}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
severe.summary <- complete.active.quarters %>%
  filter(active) %>%
  mutate(severe = ifelse(
    num.death + num.dis > 0, TRUE, FALSE
  )) %>%
  group_by(severe) %>%
  summarise(n = n()) %>%
  mutate(perc = n / sum(n) * 100)
print(severe.summary)
```

<!-- http://www.stata.com/manuals13/rclogit.pdf -->
## Processing Data

- Consider fixed-mine effects
    - Biostatisticians and epidemiologists call it "conditional logistic regression" (R, survival::clogit)
    - Suitable for panel data (e.g., our master data table)
    - Model includes mine-specific but time-invariant variables (e.g., same slope but different intercepts for different mines)

## Logistic Regression Without Fixed Effects

- Train and test on all data

```{r glm}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
print(glm.performance$table)
print(glm.performance$byClass)
```

## Logistic Regression Without Fixed Effects

- Sort result based on number of deaths

```{r glm rank death}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(glm.result %>% filter(year >= 2005) %>% arrange(desc(num.death), mine.name), 10) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
```

<!--
## Logistic Regression Without Fixed Effects

- Sort result based on model probability

```{r glm rank prob}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(glm.result %>% filter(year >= 2005) %>% arrange(desc(prob)), 10) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
```
-->

## Logistic Regression with Fixed Effects

- Randomly select half of the data to train and the other half to test

```{r fe.div}
if (!exists("fe.div.result")){load("./San Antonio/output/results_fixed_effects.RData")}
print(fe.div.performance$table)
print(fe.div.performance$byClass)
```

## Logistic Regression with Fixed Effects

- Sort result based on number of deaths

```{r fe.div rank death}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.div.result %>% filter(year >= 2005) %>% arrange(desc(num.death), mine.name), 10) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
```

## Logistic Regression with Fixed Effects

- Sort result based on model probability

```{r fe.div rank prob}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.div.result %>% filter(year >= 2005) %>% arrange(desc(prob)), 10) %>% select(
  mine.name, num.death, severe, prob, pred
) %>% mutate (mine.name = strtrim(mine.name, 40))
```

## New Era Mine

- The American Coal Company New Era Mine occupies 6 slots on the top 10 list of most days lost due to accidents

```{r top 10 days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.days.lost <- complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost), mine.name) %>% select(mine.name, year, quarter, num.days.lost)
head(top.days.lost, 10)
```

## New Era Mine

<!--- Violation trend prior to the first quarter in 2006 where model probability is 0.99-->

```{r new era viol}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1102752 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

## Simple Linear Model on Number of Days Lost

- Adjusted $R^2=0.36$

```{r simple lm of days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
num.days.lm <- lm(num.days.lost~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active))
summary(num.days.lm)$coefficients
```

@@

## Conclusion

<!-- - Causal relationship between accidents and historical data -->
- TBD
